Evaluation of performances

### 2019-12-10 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

```{r performance-results, warning=FALSE, dev = c("png", "pdf")}
results_aggr <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = recode_factor(learner_group, `XG` = "XGBOOST")) %>%
  group_by(learner_group, task.id) %>%
  # get the best performance per learner and task
  # this is better than summarise() because we can keep additional columns
  # in constrast to summariuse which only keeps the grouping columns and the
  # summarised one
  slice(which.min(rmse.test.rmse))

results_aggr %>%
  ggplot(aes(x = rmse.test.rmse, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse.test.rmse < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste(filter, ",", round(rmse.test.rmse, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse.test.rmse))

best_no_filter <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse.test.rmse))

@@

comb %>%
  ggplot(aes(x = rmse.test.rmse, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse.test.rmse))

borda <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "Borda") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse.test.rmse))

@@

comb_borda %>%
  ggplot(aes(x = rmse.test.rmse, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

perf_all_filters %>%
  ggplot(aes(x = rmse.test.rmse, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 2) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

>>>>

```{r performance-results, warning=FALSE, dev = c("png", "pdf")}
results_aggr <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = recode_factor(learner_group, `XG` = "XGBOOST")) %>%
  group_by(learner_group, task.id) %>%
  # get the best performance per learner and task
  # this is better than summarise() because we can keep additional columns
  # in constrast to summariuse which only keeps the grouping columns and the
  # summarised one
  slice(which.min(rmse_aggr))

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste(filter, ",", round(rmse_aggr, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

best_no_filter <- df_perf %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

@@

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

borda <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "Borda") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

@@

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

perf_all_filters %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 2) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```
